% !TeX program = xelatex

\documentclass[]{appsilon} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\linespread{1.13}
\initAppsilonSidebarDocument

\begin{document}

\header{Zofia}{Rogala}{Turning problems into challenges with enthusiasm and teamwork} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------
\begin{sidebar} % In the aside, each new line forces a line break	
\section{contact}
+48 508 267 612
\href{mailto:zosia.rogala@gmail.com}{zosia.rogala@gmail.com}
\href{http://linkedin.com/in/zofiarogala}{linkedin: zofiarogala}
\href{https://github.com/ZosiaRog}{github: zosiarog}
\section{languages}
Polish -- native
English -- fluent
Spanish -- fluent
Italian -- intermediate
Russian -- basic

\section{tech skills}
Python
R
Git
{\color{green} $\varheartsuit$} Linux
{\color{red} $\varheartsuit$} \LaTeX
SQL

\section{interests}
Exploring world on foot
Sailing (certified skipper)
Swing Era dances
Singing
Philosophy
\end{sidebar}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
	%------------------------------------------------
	\entry
	{2012 -- 2018}
	{Master's Degree in Mathematics}
	{University of Warsaw, Poland}
	{Individual interdisciplinary programme in Mathematics, Social Science and Psychology. Specialized in Probability and Stochastic Processes.}
	%------------------------------------------------
	\entry
	{2017 -- 2018}
	{Erasmus Programme in Mathematics}
	{University of Padova, Italy}
	{\vspace{-0.4cm}}
	%------------------------------------------------
	\entry
	{2015 -- 2017}
	{Advanced Studies in Political, Economical \& Social Sciences}
	{Phoenix Institute}
	{3-year summer programme in Vienna, Austria. Graduated magna cum laude.}
	%------------------------------------------------
\end{entrylist}



%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\vspace{0cm}
\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
{2018}
{Master Thesis: Opinion propagation in stochastic graphs}
{Padova, Italy}
{Improved Axelrod model of opinion propagation. Showed analytically that new model gives more realistic results. Implemented the model in Python.}
%------------------------------------------------
\entry
{2018}
{Summer School On-site Coordinator}
{Cracow, Poland}
{\emph{International Summer School on Integral Leadership} \\
	Worked in core organizing team. Responsible for activities programme and communication with participants, lecturers and media.}
%------------------------------------------------
\entry
{2015 -- 2016}
{Board Member for Human Resources}
{Warsaw, Poland}
{\emph{Intercollegiate Academic Society Soli Deo} \\
Coordinated HR managers from all universities. Reorganized HR structure and introduced new policy to increase member engagement.
}
%------------------------------------------------
\entry
{2014}
{Strategic Consulting Department, Intern}
{Warsaw, Poland}
{\emph{Deloitte Advisory} \\
Performed analysis and prepared market statistics for European banking. Identified and fixed errors that impacted project outcome. Prepared presentation of team's results for stakeholders. }
%------------------------------------------------
\entry
{2013}
{Volunteer Teacher of English}
{Kyrgyzstan}
{Prepared and taught 1-month English course to local university students.}

%------------------------------------------------
\entry
{2012}
{Assistant to Consul General}
{Gdansk, Poland}
{\emph{Embassy of Spain in Poland} \\
Coordinated temporary consular office in Gdansk during 2012 UEFA European Championship. Handled consular matters for Spanish citizens.  
}
\end{entrylist}


%----------------------------------------------------------------------------------------
%	CERTIFIACTES SECTION
%----------------------------------------------------------------------------------------

  \begin{tikzpicture}[remember picture,overlay]
    \node [rectangle, fill=white, anchor=south, minimum width=\paperwidth, minimum height=4.8cm, opacity=0.1] (box) at (current page.south){};
    \node [anchor=center,text width=19cm, yshift = 1.7cm] (quote1) at (box) {%
      \fontsize{12pt}{20pt}\color{header}%
      \emph{Zofia is a bright and well-organized individual with a creative approach to problem solving.}\\
	{\vspace{0.2cm}}
	\begin{flushright}
		Mark MacRae, Senior Manager, Deloitte
	\end{flushright}
	{\vspace{0.4cm}}
    };
    \node [anchor=north, text width=19cm] (quote2) at (quote1.south) {%
      \fontsize{12pt}{20pt}\color{header}%
      \emph{I'd like to emphasize Zofia's extraordinary engagement, teamwork, and responsibility. She's always curious and eager to learn. Her empathetic and open personality contributes to a fantastic atmosphere at work.}\\
	{\vspace{0.2cm}}
	\begin{flushright}
		Francisco Fernandez Fabregas, Ambassador of Spain to Poland
	\end{flushright}
    };
  \end{tikzpicture}

%0A6CA8


\end{document}
